\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.65in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{ebgaramond}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{multicol}

% Styling
\definecolor{primaryblue}{RGB}{37, 99, 235}
\definecolor{sectiongray}{RGB}{55, 65, 81}

\titleformat{\section}{\large\bfseries\color{primaryblue}}{\thesection}{0em}{}[\vspace{-0.6em}\titlerule\vspace{0.15em}]
\titleformat{\subsection}{\normalsize\bfseries\color{sectiongray}}{\thesubsection}{0em}{}

\setlist[itemize]{leftmargin=1.2em, nosep, itemsep=0pt, topsep=1pt, parsep=0pt, after=\vspace{2pt}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlength{\columnsep}{1.3em}

\hypersetup{colorlinks=true, linkcolor=primaryblue, urlcolor=primaryblue}

\pagestyle{empty}

\begin{document}

% Header
\begin{center}
    {\LARGE\bfseries\color{primaryblue} Lithos} \\[0.15em]
    {\large AI-Powered Critical Minerals Intelligence Platform} \\[0.1em]
    {\normalsize\textit{Bloomberg Terminal for Mining — Cuts Research from 2 Weeks to 2 Minutes}}
\end{center}

\vspace{-0.2em}

\begin{multicols}{2}

\section*{Product Overview}
\textbf{Lithos} automates mining research by extracting structured data from 400--500 page technical reports using LLM-powered pipelines. With 15,000+ indexed projects and instant AI analysis, we turn analyst workflows from weeks to minutes.

\subsection*{Value Proposition}
\begin{itemize}
    \item \textbf{Automated Extraction:} NPV, IRR, CAPEX, reserves from NI 43-101/JORC reports
    \item \textbf{15,000+ Projects:} Gold, copper, lithium, nickel, rare earths worldwide
    \item \textbf{AI Intelligence:} Risk analysis, comparisons, due diligence in seconds
    \item \textbf{Real-Time News:} Permitting, production, commodity price tracking
\end{itemize}

\section*{Core Features}

\subsection*{1. Project Screener}
Bloomberg-style table with advanced multi-filter system (commodity, jurisdiction, stage, NPV/IRR/CAPEX/AISC ranges), global search, bulk actions (watchlist, CSV export, comparison), conditional formatting.

\subsection*{2. Project Detail Panel}
Key metrics dashboard, inline PDF viewer for 400--500 page technical reports, resource/reserve breakdown, qualified persons, interactive maps, recent news, risk alerts, similar projects, multi-tab interface.

\subsection*{3. AI Chat}
GPT-4-powered conversational analysis: project-specific questions ("What are the main risks for Odyssey Project?"), comparative analysis, financial deep dives, document-grounded answers citing technical reports and filings.

\subsection*{4. Project Comparison}
Side-by-side analysis of 2--10 projects with percentage differences, trend indicators, detailed comparison tables, toggle filters for ESG/jurisdiction risk, export to CSV/PDF for investment committees.

\subsection*{5. Mining Agent}
Automated scraping from SEDAR, SEC EDGAR, ASX, LSE; Firecrawl-powered document processing; GPT-4 extraction pipeline; real-time progress tracking; validation across report sections; 24-hour update frequency.

\subsection*{6. Interactive Globe}
3D visualization of 15,000 projects with lat/long coordinates, commodity color coding, cluster analysis, zoom/pan for regional exploration, click-to-detail for instant analysis.

\subsection*{7. News Feed}
Project-specific news, commodity price tracking, regulatory filings, AI summarization, impact analysis (positive/neutral/negative), historical archive with search.

\subsection*{8. Company Screener}
Company database with portfolio views, aggregate metrics (total NPV, CAPEX, production), market data for public companies, management teams, company comparison.

\subsection*{9. Document Upload}
Drag-and-drop PDF upload for private NI 43-101/JORC reports, automatic extraction, user-specific private projects, secure Supabase Storage, full feature access (AI chat, comparison, sensitivity).

\subsection*{10. Sensitivity Analysis}
Real-time financial modeling with interactive sliders: commodity price scenarios, discount rate tuning (5\%--12\%), CAPEX/OPEX multipliers (1.2x--2.0x), production rate adjustments, scenario comparison (bull/base/bear).

\subsection*{11. Watchlist \& Export}
One-click watchlist, filtering to watchlisted projects, CSV export, comparison reports for investment committees, API access (roadmap).

\columnbreak

\section*{Technical Architecture}

\textbf{Frontend:} Next.js 15.2.4, TypeScript, Tailwind CSS, Radix UI + shadcn/ui, TanStack Table, Recharts

\textbf{Backend:} Supabase (PostgreSQL), Supabase Auth, OpenAI GPT-4, Firecrawl API, News API

\textbf{Data Sources:} SEDAR (Canada), SEC EDGAR (US), ASX (Australia), LSE (UK), company websites, news APIs

\textbf{Extraction Pipeline:} Firecrawl API extracts text from 400--500 page PDFs $\rightarrow$ GPT-4 structured extraction prompts $\rightarrow$ Multi-pass validation $\rightarrow$ PostgreSQL storage with geospatial indexing

\section*{Key Differentiators}

\begin{itemize}
    \item \textbf{Automated Extraction at Scale:} Only platform extracting structured data from 400--500 page technical reports automatically
    \item \textbf{AI-First Architecture:} Built for LLMs from day one with document-grounded conversational intelligence
    \item \textbf{Real-Time Updates:} 24-hour processing cycle for new filings vs. quarterly updates from competitors
    \item \textbf{Modern UX:} Bloomberg-inspired interface with advanced filtering, bulk actions, and export capabilities
    \item \textbf{Vertical Focus:} Deep mining expertise and technical report knowledge vs. horizontal data platforms
\end{itemize}

\section*{Competitive Position}

\textbf{S\&P Capital IQ / Bloomberg:} Have company financials and commodity prices but no project-level technical data or automated extraction from technical reports. Analysts still read 500-page reports manually.

\textbf{Mining Databases (SNL, Wood Mackenzie):} Static datasets updated quarterly with clunky legacy interfaces. No AI, no real-time extraction, no conversational intelligence.

\textbf{Lithos Advantage:} Only platform combining automated extraction, AI analysis, real-time updates, and modern UI in one integrated solution.

\vspace{0.5em}

\begin{center}
\textit{Lithos — Turning weeks of mining research into seconds.} \\
\texttt{www.lithos.ai} $\cdot$ \texttt{team@lithos.ai}
\end{center}

\end{multicols}

\end{document}
